Higgs Assisted Razor Search for Higgsinos at a 100 TeV $pp$ Collider

### 2019-08-09 main.tex

\documentclass[a4paper,11pt]{article}
 \providecommand{\tightlist}{%
     \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{graphicx}
\usepackage{jheppub} 
\usepackage{comment} 
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{slashed}
\usepackage{pgfplots}
\usepackage{booktabs, longtable}
\usepackage{microtype}
\usepackage{soul}
\bibliographystyle{JHEP.bst}

@@

\abstract{% 
  A 100 TeV proton-proton collider will be an extremely effective way to probe
  the electroweak sector of the Minimal Supersymmetric Standard Model (MSSM).
  In this paper, we describe a search strategy  for discovering pair-produced
  Higgsino-like next-to-lightest supersymmetric particles (NLSPs)  at a 100 TeV
  hadron collider that decay to Bino-like lightest supersymmetric particle
  (LSP) via intermediate $Z$ and SM Higgs boson that in turn decay to a pair
  of leptons and a pair of $b$-quarks respectively: $\N_{2}\N_{3} \rightarrow
  (Z\N_1)(h\N_1)\rightarrow bb\ell\ell+\N_1\N_1$. In addition, we examine the
  potential for machine learning techniques to boost the power of our searches.
  Using this analysis, Higgsinos up to 1.4 TeV can be discovered  at 5 $\sigma$ level for a Bino with
  mass of about
  0.9 TeV using 3000 fb$^{-1}$ of data.  Additionally, Higgsinos up to 1.8
  TeV can be excluded  at 95\% C.L. for a Bino with mass of about 1.4 TeV。   This search
  channel extends the multi-lepton search limits, especially in the region
  where the mass difference between the Higgsino NLSPs and the Bino LSP is small.
}

\begin{document} 
\maketitle
%\flushbottom

>>>>

\documentclass[a4paper,11pt]{article}
 \providecommand{\tightlist}{%
     \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{graphicx}
\usepackage{jheppub} 
\usepackage{comment} 
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{slashed}
\usepackage{pgfplots}
\pgfplotsset{compat=1.14}
\usepackage{booktabs, longtable}
\usepackage{microtype}
\usepackage{soul}
\bibliographystyle{JHEP.bst}

@@

\abstract{%
  A 100 TeV proton-proton collider will be an extremely effective way to probe
  the electroweak sector of the Minimal Supersymmetric Standard Model (MSSM).  In
  this paper, we describe a search strategy for discovering pair-produced
  Higgsino-like next-to-lightest supersymmetric particles (NLSPs) at a 100 TeV
  hadron collider that decay to Bino-like lightest supersymmetric particle (LSP)
  via intermediate $Z$ and SM Higgs boson that in turn decay to a pair of leptons
  and a pair of $b$-quarks respectively: $\N_{2}\N_{3} \rightarrow
  (Z\N_1)(h\N_1)\rightarrow bb\ell\ell+\N_1\N_1$. In addition, we examine the
  potential for machine learning techniques to boost the power of our searches.
  Using this analysis, Higgsinos up to 1.4 TeV can be discovered  at 5 $\sigma$
  level for a Bino with mass of about 0.9 TeV using 3000 fb$^{-1}$ of data.
  Additionally, Higgsinos up to 1.8 TeV can be excluded  at 95\% C.L. for Binos
  with mass of about 1.4 TeV. This search channel extends the multi-lepton search
  limits, especially in the region where the mass difference between the Higgsino
  NLSPs and the Bino LSP is small.
}

\begin{document}

\maketitle
